### 2013-06-25 latex/SupportingText.tex
Added to more tables to SupportingText.tex with values from NormalizationValuesByPercentDataCoverageAndGenerous.txt.

>>>>

\begin{center}
\footnotesize
\begin{tabular}{lcccccccc}
&  \multicolumn{2}{c}{Empirical} & ~~~& \multicolumn{2}{c}{Theoretical}\\\cline{2-3}\cline{5-6}
Residue & max_theo_100 & max_emp_100 & & max_theo_97 & max_emp_97 & & max_theo 80 & max_emp_80 & & max_theo_gen & max_emp_gen \\
\hline Alanine   & $138$ & $121$ & & $129$ & $121$ & & $128$ & $121$ & & $132$ & $121$\\
Arginine         & $285$ & $265$ & & $274$ & $265$ & & $274$ & $265$ & & $280$ & $265$\\
Asparagine       & $204$ & $187$ & & $195$ & $187$ & & $193$ & $187$ & & $199$ & $187$\\
Aspartate        & $204$ & $187$ & & $195$ & $187$ & & $193$ & $187$ & & $199$ & $187$\\
Cysteine         & $169$ & $148$ & & $167$ & $148$ & & $157$ & $133$ & & $167$ & $148$\\
Glutamine        & $234$ & $214$ & & $225$ & $214$ & & $224$ & $214$ & & $228$ & $214$\\
Glutamate        & $233$ & $214$ & & $223$ & $214$ & & $224$ & $214$ & & $227$ & $214$\\
Glycine          & $114$ & $\phantom{0}97$ & & $104$ & $97$ & & $104$ & $97$ & & $109$ & $97$\\
Histidine        & $213$ & $216$ & & $209$ & $216$ & & $209$ & $216$ & & $209$ & $216$\\
Isoleucine       & $208$ & $195$ & & $197$ & $195$ & & $196$ & $195$ & & $201$ & $195$\\
Leucine          & $211$ & $191$ & & $201$ & $191$ & & $199$ & $191$ & & $205$ & $191$\\
Lysine           & $246$ & $230$ & & $236$ & $230$ & & $235$ & $229$ & & $240$ & $230$\\
Methionine       & $227$ & $203$ & & $224$ & $203$ & & $218$ & $203$ & & $226$ & $203$\\
Phenylalanine    & $251$ & $228$ & & $240$ & $228$ & & $236$ & $226$ & & $244$ & $228$\\
Proline          & $166$ & $154$ & & $159$ & $154$ & & $157$ & $154$ & & $164$ & $154$\\
Serine           & $161$ & $143$ & & $155$ & $143$ & & $150$ & $143$ & & $158$ & $143$\\
Threonine        & $182$ & $163$ & & $172$ & $163$ & & $171$ & $161$ & & $176$ & $163$\\
Tryptophan       & $295$ & $264$ & & $285$ & $264$ & & $282$ & $262$ & & $293$ & $264$\\
Tyrosine         & $274$ & $255$ & & $263$ & $255$ & & $262$ & $255$ & & $266$ & $255$\\
Valine           & $184$ & $166$ & & $174$ & $165$ & & $173$ & $165$ & & $177$ & $166$\\
\hline
\end{tabular}
\end{center}

\begin{center}
\footnotesize
\begin{tabular}{lcccccccc}
&  \multicolumn{2}{c}{Empirical} & ~~~& \multicolumn{2}{c}{Theoretical}\\\cline{2-3}\cline{5-6}
Residue & pop_97 & pop_80 \\
\hline Alanine   & $4$ & $47$ \\
Arginine         & $2$ & $23$ \\
Asparagine       & $2$ & $15$ \\
Aspartate        & $3$ & $20$ \\
Cysteine         & $0$ & $\phantom{0}5$ \\
Glutamine        & $2$ & $18$ \\
Glutamate        & $3$ & $34$ \\
Glycine          & $2$ & $15$ \\
Histidine        & $1$ & $\phantom{0}9$ \\
Isoleucine       & $6$ & $40$ \\
Leucine          & $7$ & $59$ \\
Lysine           & $3$ & $27$ \\
Methionine       & $0$ & $\phantom{0}8$ \\
Phenylalanine    & $2$ & $20$ \\
Proline          & $7$ & $80$ \\
Serine           & $2$ & $27$ \\
Threonine        & $3$ & $33$ \\
Tryptophan       & $0$ & $\phantom{0}8$ \\
Tyrosine         & $2$ & $18$ \\
Valine           & $7$ & $50$ \\
\hline
\end{tabular}
\end{center}
